\documentclass[solution,12pt]{exam}
%\printanswers
\usepackage{amsmath,amssymb}
\newcommand{\tsp}{{\sf TSP}}
\begin{document}

\hrule
\vspace{3mm}
\noindent 
{\sf IITM-CS6100 : Topics in Design and analysis of Algorithms  \hfill Given on: Mar 23}
\vspace{3mm}\\
\noindent 
{\sf Problem Set \#2 \hfill Due on : May 15, 23:55}
{\hfill \sf Evaluation Due on : May 20 }
\vspace{3mm}
\hrule
{\small
\begin{itemize}
\item Turn in your solutions electronically at the moodle page. The submission should be a pdf file typeset either using     LaTeX or any other software that generates pdf. No handwritten solutions are accepted. 
\item Collaboration is encouraged, but all write-ups must be done
  individually and independently. For each question, you are required to mention the set of collaborators, if any.  
 \item Submissions will be checked for {\bf plagiarism}. Each case of plagiarism will be reported to the institute disciplinary committee (DISCO). 
\end{itemize}}
\hrule
\vspace{3mm}
%\noindent {\sc Author :} Name. \\[1mm]
%\noindent {\sc Collaborators :} \\
%\hrule
\begin{questions}
%\begin{solution}
%{\bf Collaborators}:\\ 
%Write solutions  afer uncommenting the lines above and below.
%\end{solution}
\question[8]   Let $P = \{p_1,\ldots, p_n\}$ be a set of $n$ points from the unit square $[0,1]^2$. A triangulation $\tau$ of $P$ is a maximal planar graph with $P$ as the vertex set (i.e., the locations of points in $P$ should be an embedding of the graph). A minimum weight triangulation (denoted by mwt) is a triangulation with minimum total edge weight.  Let $MWT$ denote the corresponding Euclidean functional. The convex hull (denoted by $CH$) of $P$ is the smallest convex set (i.e. polygon) containing $P$. Let $|CH(P)|$ denote the number of vertices in the convex hull of $P$.  Suppose $Q_1,Q_2, Q_3$ and $Q_4$ be a partition of $[0,1]^2$ of equal sized squares. Show that
$$ MWT(P, [0,1]^2) \le \sum_{i=1}^4 MWT(P\cap Q_i, Q_i) + \sum_{i=1}^4 O(|CH(P\cap Q_i)|).$$
\question[16] In the vehicle routing problem, we are given a set of depots $D = \{d_1,\ldots, d_k\}$ from $[0,1]^d$ and a set of $n$ points  $ P =\{p_1,\ldots, p_n\}$  (called customers) which are again  points from $[0,1]^d$. The job is to compute minimum cost $k$ vertex disjoint cycles such that every cycle has exactly one depot and every depot is in exactly one cycle.  Let $MDP$ denote the corresponding Euclidean functional. 
\begin{parts}
\part[7] Formally define the functional $MDP$.     Prove that $MDP$ is subadditive but not superadditive.
\part[9] Define a canonical  boundary functional $MDP_B$ for $MDP$ and show that it is superadditive. Show that the boundary functional is also a  smooth Euclidean functional. 
\end{parts}
 

%\begin{solution}
%{\bf Collaborators}:\\ 
%Write solutions  afer uncommenting the lines above and below.
%\end{solution}


\question[6] Refer to phase 3 of the algorithm for computing Hamiltonian cycle given in Page 6 of  Frieze's survey.   Show that for any tractable graph, the phase 3 of the algorithm always succeeds in computing a Hamiltonian cycle, if exists. 
%\begin{solution}
%{\bf Collaborators}:\\ 
%Write solutions  afer uncommenting the lines above and below.
%\end{solution}
 
%\begin{solution}
%{\bf Collaborators}:\\ 
%Write solutions  afer uncommenting the lines above and below.
%\end{solution}

\end{questions}


\end{document}